Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex
Added git repo

The accompanying artifact \apt{what is the state of that? Depending on conference preferences,
  should give a URL or other pointer.} \sna{Git repo is currently private, I think. I didn't see much
  in the way of conference preferences on a quick glance, but I'll look again in the morning.}
contains formal definitions (in Coq) of our
properties, plus our testing framework.  It does not include proofs, since
we use Coq primarily for the QuickChick testing library and to
ensure that our definitions are unambiguous.  Formal proofs are left
as future work.

@@

\sna{Maybe a quick example or even two would be of benefit here.}
For better performance, we instead maintain a single ``post-call taint''
execution that executes in parallel with the original. Everytime a function returns
with elements containing tainted data\apt{I don't understand what that is}, the test process sets those elements
to random values in the tainted execution. So, at any given time, we need only simulate
(1) the original execution, (2) the tainted execution, and (3) one
variant execution for each call on the call stack. This approach
makes testing longer executions substantially faster, at the cost of making it
harder to identify which call is the source of a failure.

>>>>

The accompanying artifact \footnote{https://github.com/SNoAnd/stack-safety}
contains formal definitions (in Coq) of our
properties, plus our testing framework.  It does not include proofs, since
we use Coq primarily for the QuickChick testing library and to
ensure that our definitions are unambiguous.  Formal proofs are left
as future work.

@@

For better performance, we instead maintain a single execution that combines
all of the variants that would be spawned at returns.
So, at any given time, we need only simulate
(1) the original execution, (2) the tainted execution, and (3) one
variant execution for each call on the call stack. This approach
makes testing longer executions substantially faster, at the cost of making it
harder to identify which call is the source of a failure.
